The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2017-07-18 paper/ms.tex
Add figures for halo pages

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{halos_page.eps}
\caption{Another example of a ``simulation page,'' except showing halos from a cosmological simulation instead of epochs. Slider bars allow exploration of different halos, and buttons near the top choose different projection axes. The figures link to the page for the files for the corresponding halo ID. This particular page is linked at \url{http://gcmc.hub.yt/omega500/non_radiative_1.0005/index.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{halo_page.eps}
\caption{A portion of a ``halo page,'' showing the details of the halo information and the slice data for this particular halo. This particular page is linked at \url{http://gcmc.hub.yt/omega500/non_radiative_1.0005/00086.html}.}
\end{center}
\end{figure*}
